\begin{abstract}
\addcontentsline{toc}{section}{Abstract}
This project presents an IoT-based vital sign monitoring system with conversational health data access, designed to address challenges in personal health monitoring and data interpretation. The system uses IoT sensors to collect vital health parameters and provides an intuitive natural language interface that allows users to query and understand their health data through simple conversations, making complex health information more accessible to non-technical users.

The implementation integrates Arduino-based IoT sensors including an ECG sensor, heart rate monitor, pulse sensor, and body temperature sensor for comprehensive vital sign monitoring with a user-friendly dashboard. These sensors collect physiological data such as cardiac electrical activity, beats per minute, blood flow patterns, and core body temperature. The system utilizes Next.js for the frontend interface, FastAPI for backend services, and a Retrieval-Augmented Generation (RAG) pipeline built on LangChain and OpenAI's GPT models. This architecture enables natural language processing capabilities that allow users to interact conversationally with their health data while ensuring security measures for data privacy and compliance with healthcare regulations.

This IoT-driven approach to health monitoring is a significant advancement in personal healthcare management by combining sensor technology with conversational AI. The system demonstrates how IoT sensors paired with natural language interfaces can transform health data into actionable insights, potentially improving health outcomes through better understanding and management of vital signs without requiring specialized technical knowledge.
\end{abstract}
\newpage 