\section{METHODOLOGY}

\subsection{Implementation Tasks}

\begin{enumerate}

\item \textbf{Frontend Development}
\begin{itemize}
    \item Design the user interface using \textbf{Next.js} with \textbf{TailwindCSS} and \textbf{shadcn/ui} for a responsive, modular experience.
    \item Build a real-time dashboard to visualize health metrics such as SpO2, heart rate, ECG, and temperature.
    \item Integrate Supabase Auth to enable secure user login and session handling.
\end{itemize}

\item \textbf{Backend Development}
\begin{itemize}
    \item Set up a \textbf{FastAPI} server to handle incoming sensor data and expose RESTful endpoints.
    \item Use a \textbf{PostgreSQL} database (hosted via Supabase) to store and manage health data securely.
    \item Develop APIs for data submission, retrieval, and query handling.
\end{itemize}

\item \textbf{IoT Sensor Integration}
\begin{itemize}
    \item Use an \textbf{Arduino UNO R3} to interface with all biomedical sensors and read analog/digital inputs.
    \item Employ an \textbf{ESP8266 Wi-Fi module} to transmit data to the cloud via HTTP or MQTT.
    \item Configure periodic data sampling and preprocessing before cloud transmission.
\end{itemize}

\item \textbf{AI Integration}
\begin{itemize}
    \item Integrate a conversational AI interface using \textbf{LangChain} and \textbf{GPT-4/GPT-4o}.
    \item Allow users to query their health records through natural language using a Text-to-SQL pipeline.
    \item Provide automated health summaries and anomaly detection powered by AI.
\end{itemize}

\end{enumerate}
